\documentclass[lettersize,journal]{IEEEtran}

\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{balance}

\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}

\newtheorem{assumption}{Assumption}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\sat}{\operatorname{sat}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\R}{\mathbb{R}}

\begin{document}

\title{Resilient Cooperative Guidance Under Hybrid DoS and False-Data Injection Attacks}

\author{Author~Name
\thanks{This manuscript draft records a possible research idea for resilient cooperative guidance under hybrid cyber attacks.}}

\markboth{Draft Manuscript,~June~2026}%
{Resilient Cooperative Guidance Under Hybrid DoS and False-Data Injection Attacks}

\maketitle

\begin{abstract}
This draft presents a unified treatment for denial-of-service (DoS) and false-data injection (FDI) attacks in networked cooperative guidance of multiple flight vehicles. DoS attacks remove communication links and make neighbor information unavailable, whereas FDI attacks keep the communication channel active but corrupt the transmitted guidance variables. To handle the two attack modes within a single framework, a trusted-graph isolation mechanism is proposed. The mechanism first detects link availability, then evaluates data credibility through a multi-evidence trust mechanism that combines physical feasibility, group-consistency clustering, and windowed distribution divergence. Once a link is judged to be corrupted by FDI, it is removed from the cooperative guidance graph rather than softly blended with a substitute value. A resilient impact-time synchronization error is then defined on the remaining trusted graph. Exponential and fixed-time convergence conditions are derived in terms of accumulated trusted connectivity after DoS blocking and FDI isolation.
\end{abstract}

\begin{IEEEkeywords}
Cooperative guidance, denial-of-service attack, false-data injection attack, resilient control, virtual leader, finite-time convergence.
\end{IEEEkeywords}

\section{Introduction}
\IEEEPARstart{N}{etworked} cooperative guidance enables multiple flight vehicles to coordinate their impact times by exchanging local guidance variables, such as time-to-go estimates or impact-time errors. In an ideal communication environment, this problem can be converted into a consensus problem over a connected graph. However, the communication graph may be damaged by cyber attacks. In particular, DoS attacks interrupt communication links and make neighbor information unavailable, whereas FDI attacks inject corrupted data into still-active communication links. These two attack modes create different difficulties: DoS causes missing information, while FDI causes misleading information.

A direct zero-bias strategy can be used during DoS intervals. Under such a strategy, the cooperative terms associated with disconnected links are removed, and the guidance law degenerates to a local or proportional-navigation-like behavior. This approach is conservative and useful for stability preservation, but it suspends part of the cooperation and may introduce discontinuities in the command. Conversely, a single-predictor residual detector may attenuate simple FDI signals but can be unreliable in cooperative guidance because target maneuvers, modeling errors, field-of-view constraints, and intermittent DoS intervals can all enlarge the prediction residual.

This draft therefore proposes a unified trusted-graph framework. The central idea is to decide which neighbor information is allowed to enter the cooperative guidance law. DoS is handled through link-availability indicators, and detected FDI is handled by removing the corrupted link from the cooperative graph. A zero-bias fallback is used when the remaining trusted graph is not connected, so unavailable or corrupted links cannot inject positive energy into the impact-time disagreement dynamics.

The one-sentence argument of this draft is as follows: in cooperative guidance under hybrid DoS and FDI attacks, the impact-time synchronization error can be driven to zero before interception by isolating unavailable or corrupted links and by requiring sufficient accumulated trusted connectivity before impact.

\section{Cooperative Guidance Variable}

Consider $N$ flight vehicles intercepting a common target. The communication topology is described by
\begin{equation}
    \mathcal{G}(t)=\{\mathcal{V},\mathcal{E}(t),A(t)\},
\end{equation}
where $\mathcal{V}=\{1,2,\ldots,N\}$ is the vehicle set, $\mathcal{E}(t)$ is the communication edge set, and $A(t)=[a_{ij}(t)]$ is the adjacency matrix. If vehicle $i$ can receive information from vehicle $j$, then $a_{ij}(t)>0$; otherwise $a_{ij}(t)=0$.

The main cooperative variable is selected as the time-to-go estimate. Let
\begin{equation}
    t_{go,i}(t)=t_{f,i}(t)-t
\end{equation}
denote the remaining flight time of vehicle $i$, where $t_{f,i}$ is its predicted impact time. Simultaneous interception requires
\begin{equation}
    t_{go,1}(t)=t_{go,2}(t)=\cdots=t_{go,N}(t).
\end{equation}
Without attacks, the local cooperative error can be defined as
\begin{equation}
    e_i(t)=
    \sum_{j\in\mathcal{N}_i(t)}
    a_{ij}(t)\left[t_{go,i}(t)-t_{go,j}(t)\right],
    \label{eq:nominal_error}
\end{equation}
where $\mathcal{N}_i(t)$ is the neighbor set of vehicle $i$.

\section{Hybrid DoS and FDI Attack Model}

Let $y_{ij}(t)$ denote the information received by vehicle $i$ from vehicle $j$. Under hybrid DoS and FDI attacks, the received signal is modeled as
\begin{equation}
    y_{ij}(t)
    =
    \gamma_{ij}(t)\left[x_j(t)+f_{ij}(t)\right],
    \label{eq:hybrid_model}
\end{equation}
where $x_j(t)$ is the true transmitted information of vehicle $j$, $f_{ij}(t)$ is the FDI signal injected into link $(j,i)$, and $\gamma_{ij}(t)$ is the DoS switching signal:
\begin{equation}
    \gamma_{ij}(t)=
    \begin{cases}
        1, & \text{link }(j,i)\text{ is available},\\
        0, & \text{link }(j,i)\text{ is blocked by DoS}.
    \end{cases}
    \label{eq:dos_switch}
\end{equation}
For time-to-go coordination, \eqref{eq:hybrid_model} becomes
\begin{equation}
    y_{ij}(t)
    =
    \gamma_{ij}(t)
    \left[t_{go,j}(t)+f_{ij}(t)\right].
    \label{eq:tgo_attack}
\end{equation}

This model covers three cases. If $\gamma_{ij}=1$ and $f_{ij}=0$, the link is normal. If $\gamma_{ij}=1$ and $f_{ij}\ne0$, the link is active but corrupted by FDI. If $\gamma_{ij}=0$, the link is unavailable due to DoS.

\section{FDI Treatment: Multi-Evidence Trust Evaluation}

FDI attacks should not be handled as missing data because the corrupted signal is still received. A direct approach is to compare the received information with a local prediction. Let $\hat t_{go,j}^{\,i}(t)$ denote the prediction of vehicle $j$'s time-to-go maintained by vehicle $i$. The residual is
\begin{equation}
    r_{ij}(t)=y_{ij}(t)-\hat t_{go,j}^{\,i}(t).
    \label{eq:residual}
\end{equation}
However, a detector based only on $r_{ij}(t)$ is fragile in cooperative guidance. Target maneuvers, modeling errors, field-of-view constraints, previous DoS intervals, and inaccurate time-to-go approximation can all enlarge the residual even when no attack exists. Conversely, an intelligent attacker may inject data that remain close to the predictor and therefore bypass a single residual threshold. For this reason, the residual is treated only as one weak evidence source, and the credibility of each link is evaluated by a multi-evidence trust mechanism.

The proposed FDI treatment answers three questions for each received neighbor datum:
\begin{itemize}
    \item Is the datum physically feasible under the engagement and guidance constraints?
    \item Is the datum consistent with the information reported by other neighbors?
    \item Does the recent residual distribution deviate from the nominal residual distribution?
\end{itemize}
The three answers are converted into continuous trust scores and fused into the final link trust weight $\rho_{ij}(t)\in[0,1]$.

\subsection{Physical Feasibility Evidence}

The first evidence source uses guidance-domain constraints instead of a precise predictor. Based on the last trusted state of vehicle $j$, the maximum speed or acceleration, the admissible field-of-view region, and the remaining range, vehicle $i$ constructs a feasible interval for the neighbor's time-to-go:
\begin{equation}
    t_{go,j}(t)
    \in
    \left[
    \underline t_{go,j}^{\,i}(t),
    \overline t_{go,j}^{\,i}(t)
    \right].
    \label{eq:physical_interval}
\end{equation}
If the received value lies outside this interval, it violates basic engagement feasibility and is strongly suspicious. The physical trust score can be defined as
\begin{equation}
    \rho_{ij}^{\mathrm{phy}}(t)=
    \begin{cases}
        1, &
        y_{ij}(t)\in
        \left[
        \underline t_{go,j}^{\,i}(t),
        \overline t_{go,j}^{\,i}(t)
        \right],\\
        \epsilon_{\rho}, & \text{otherwise},
    \end{cases}
    \label{eq:physical_trust}
\end{equation}
where $0<\epsilon_{\rho}\ll1$ avoids an unnecessarily hard rejection. This layer is robust to moderate prediction errors because it only checks whether the received datum is physically possible.

\subsection{Group-Consistency or GMM Evidence}

The second evidence source uses the redundancy of the multi-vehicle system. Under normal cooperation, the information reported by neighboring vehicles should be mutually consistent. Define a feature vector
\begin{equation}
    \bm{\xi}_j(t)
    =
    \begin{bmatrix}
    t_{go,j}(t) &
    \dot t_{go,j}(t) &
    q_j(t) &
    \dot q_j(t)
    \end{bmatrix}^{T},
    \label{eq:feature_vector}
\end{equation}
where $q_j$ and $\dot q_j$ denote line-of-sight-related variables. The neighbor feature set observed by vehicle $i$ is
\begin{equation}
    \mathcal{X}_i(t)=
    \left\{
    \bm{\xi}_{\ell}(t):\ell\in\mathcal{N}_i(t)
    \right\}.
    \label{eq:gmm_dataset}
\end{equation}
A Gaussian mixture model can cluster $\mathcal{X}_i(t)$ into a normal component and a suspicious component. The corresponding trust score is the belief that vehicle $j$ belongs to the normal component:
\begin{equation}
    \rho_{ij}^{\mathrm{gmm}}(t)
    =
    \Pr\left(
    \bm{\xi}_j(t)\in\mathcal{C}_{\mathrm{normal}}
    \mid
    \mathcal{X}_i(t)
    \right).
    \label{eq:gmm_trust}
\end{equation}
This idea follows the logic of clustering-based secure state estimation: rather than assuming a known attack form, the detector lets the data separate normal and abnormal information.

If a full GMM is too costly or the number of neighbors is small, a median-consistency score can be used instead:
\begin{equation}
    d_{ij}^{\mathrm{med}}(t)
    =
    \left|
    y_{ij}(t)
    -
    \operatorname{median}_{\ell\in\mathcal{N}_i(t)}
    y_{i\ell}(t)
    \right|,
    \label{eq:median_distance}
\end{equation}
\begin{equation}
    \rho_{ij}^{\mathrm{grp}}(t)
    =
    \exp\left[-\kappa_g d_{ij}^{\mathrm{med}}(t)\right],
    \quad \kappa_g>0.
    \label{eq:group_trust}
\end{equation}
The larger the deviation from the group-consistent value is, the lower the trust becomes.

\subsection{Windowed Distribution Evidence}

The third evidence source evaluates the recent statistical behavior of the residual. This is important because FDI attacks may be slow, intermittent, or small enough to avoid a single-time threshold. Define a residual window
\begin{equation}
    \mathcal{R}_{ij}^{L}(t)
    =
    \left\{
    r_{ij}(t-L+1),\ldots,r_{ij}(t)
    \right\},
    \label{eq:residual_window}
\end{equation}
where $L$ is the window length. Let $\mathcal{P}_{ij}^{L}(t)$ be the empirical distribution of this window and let $\mathcal{P}_{ij}^{0}$ be the nominal residual distribution obtained from attack-free data or from a recently trusted window. A Kullback--Leibler divergence score is
\begin{equation}
    D_{ij}^{\mathrm{KL}}(t)
    =
    D_{\mathrm{KL}}
    \left(
    \mathcal{P}_{ij}^{L}(t)
    \|
    \mathcal{P}_{ij}^{0}
    \right).
    \label{eq:kld_score}
\end{equation}
The distribution-based trust score is then
\begin{equation}
    \rho_{ij}^{\mathrm{kl}}(t)
    =
    \exp\left[-\kappa_{kl}D_{ij}^{\mathrm{KL}}(t)\right],
    \quad \kappa_{kl}>0.
    \label{eq:kld_trust}
\end{equation}
A short window reacts quickly but may create more false alarms, whereas a long window is smoother but slower. Thus, $L$ should be selected according to the expected attack duration and guidance update rate.

\subsection{Trust Fusion and Smoothing}

The final raw trust score is obtained by fusing the three evidence channels:
\begin{equation}
    \bar{\rho}_{ij}(t)
    =
    \sat_{[0,1]}
    \left(
    \rho_{ij}^{\mathrm{phy}}(t)
    \rho_{ij}^{\mathrm{gmm}}(t)
    \rho_{ij}^{\mathrm{kl}}(t)
    \right).
    \label{eq:fused_trust}
\end{equation}
If the median-consistency score is used instead of GMM, $\rho_{ij}^{\mathrm{gmm}}$ in \eqref{eq:fused_trust} is replaced by $\rho_{ij}^{\mathrm{grp}}$.

To avoid abrupt command changes caused by sudden trust switching, the implemented trust weight is filtered as
\begin{equation}
    \dot{\rho}_{ij}(t)
    =
    -a_{\rho}
    \left[
    \rho_{ij}(t)-\bar{\rho}_{ij}(t)
    \right],
    \quad a_{\rho}>0.
    \label{eq:trust_filter}
\end{equation}
The resulting $\rho_{ij}(t)$ is a continuous credibility weight. A value close to one means that the received information is physically feasible, group-consistent, and distributionally normal. A value close to zero means that the link is likely corrupted by FDI. In the control layer, this continuous score is converted into the binary isolation variable $\sigma_{ij}(t)$ used in \eqref{eq:fdi_isolation}.

\begin{remark}
During a DoS interval, no new neighbor data are available. Therefore, FDI evidence is frozen or propagated from the last trusted value, and the corresponding link is removed from the trusted graph through $\gamma_{ij}=0$. This separation avoids confusing missing data with corrupted data.
\end{remark}

\section{DoS Treatment: Link Removal and Zero-Bias Fallback}

DoS attacks make neighbor information unavailable. In the proposed trusted-graph formulation, a DoS-blocked link is removed from the cooperative graph by setting $\gamma_{ij}(t)=0$. The corresponding adjacency entry $a_{ij}^r(t)$ is then zero, so the unavailable datum cannot enter the cooperative guidance command.

This link-removal rule is conservative but important for stability. If no trusted neighbor is available for vehicle $i$, the cooperative term is set to zero and the vehicle follows the baseline guidance command. In impact-time coordinates, this means that no unverified neighbor reference is injected into the disagreement dynamics during the DoS interval.

For implementation smoothing, a virtual-leader reference $t_{go,v,ij}(t)$ may still be propagated from the last trusted value:
\begin{equation}
    t_{go,v,ij}(t_d)=y_{ij}(t_d^-),\qquad
    \dot t_{go,v,ij}(t)=-1.
    \label{eq:virtual_hold}
\end{equation}
However, this reference is allowed to affect the cooperative command only if it satisfies a nonexpansive safety condition. Otherwise, the disconnected edge remains removed. The zero-bias fallback is therefore the default stability-preserving action under DoS.

\section{Trusted Graph Construction by Link Isolation}

The detection layer is used only to decide whether a received datum is allowed to enter the cooperative guidance law. Once an FDI attack is detected on link $(j,i)$, the link is removed from the cooperative graph instead of being softly blended with a substitute value. Define the binary isolation variable
\begin{equation}
    \sigma_{ij}(t)=
    \begin{cases}
        1, & \text{link }(j,i)\text{ is judged trustworthy},\\
        0, & \text{FDI is detected on link }(j,i).
    \end{cases}
    \label{eq:fdi_isolation}
\end{equation}
The trusted adjacency entry is
\begin{equation}
    a_{ij}^{r}(t)
    =
    a_{ij}\gamma_{ij}(t)\sigma_{ij}(t),
    \label{eq:trusted_adjacency}
\end{equation}
and the resulting trusted graph is denoted by $\mathcal{G}_r(t)=(\mathcal{V},\mathcal{E}_r(t))$. Thus, DoS and detected FDI have the same effect at the control layer: the corresponding edge is excluded. If several outgoing links of the same sender are detected as corrupted, a conservative node-isolation rule may also be used:
\begin{equation}
    a_{ij}^{r}(t)
    =
    a_{ij}\gamma_{ij}(t)\sigma_i(t)\sigma_j(t),
    \label{eq:node_isolation}
\end{equation}
where $\sigma_j(t)=0$ removes node $j$ from the cooperative graph. The main analysis below is stated for link isolation; node isolation follows by applying the same proof to the remaining normal-node subgraph.

Let
\begin{equation}
    T_i(t)=t+t_{go,i}(t)
    \label{eq:impact_time}
\end{equation}
be the predicted impact time of vehicle $i$. The resilient synchronization error is defined on the trusted graph as
\begin{equation}
    e_i^{r}(t)
    =
    \sum_{j\in\mathcal{N}_i}
    a_{ij}^{r}(t)
    \left[T_i(t)-T_j(t)\right].
    \label{eq:resilient_error}
\end{equation}
Equivalently, with $T=[T_1,\ldots,T_N]^\top$,
\begin{equation}
    e^{r}(t)=L_r(t)T(t),
    \label{eq:trusted_laplacian_error}
\end{equation}
where $L_r(t)$ is the Laplacian matrix of $\mathcal{G}_r(t)$. In this form, corrupted data do not appear in the guidance law after detection.

\begin{remark}
The virtual-leader variable can still be used for trajectory smoothing or for local fallback during long DoS intervals, but it is not required for excluding FDI data from the stability proof. The rigorous convergence statement below relies on edge removal and trusted-graph connectivity rather than on a soft reconstruction of corrupted neighbor information.
\end{remark}

\section{Resilient Cooperative Guidance Law}

The cooperative guidance objective is to regulate the predicted impact times $T_i$. At the abstract synchronization level, the trusted-graph feedback can be written as
\begin{equation}
    \dot T
    =
    -k L_r(t)T,
    \quad k>0,
    \label{eq:linear_sync}
\end{equation}
for an exponentially convergent design. A fixed-time alternative is
\begin{equation}
    \dot T_i
    =
    -k_1
    \sum_{j\in\mathcal{N}_i}
    a_{ij}^{r}
    \operatorname{sig}^{\alpha}(T_i-T_j)
    -k_2
    \sum_{j\in\mathcal{N}_i}
    a_{ij}^{r}
    \operatorname{sig}^{\beta}(T_i-T_j),
    \label{eq:fixed_time_sync}
\end{equation}
where $k_1,k_2>0$, $0<\alpha<1$, $\beta>1$, and $\operatorname{sig}^{\mu}(x)=|x|^\mu\operatorname{sgn}(x)$. The actual normal-acceleration command is then selected to realize the desired change of $T_i$ through the guidance geometry:
\begin{equation}
    \bm a_i
    =
    \bm a_i^{\mathrm{PNG}}
    +
    \bm a_i^{\mathrm{coop}},
    \label{eq:guidance_command}
\end{equation}
where $\bm a_i^{\mathrm{PNG}}$ is the baseline interception term and $\bm a_i^{\mathrm{coop}}$ implements either \eqref{eq:linear_sync} or \eqref{eq:fixed_time_sync} through the local relation between normal acceleration and $\dot T_i$.

\begin{assumption}[Impact-time control channel]
For each non-isolated normal vehicle, the cooperative acceleration can realize the desired $\dot T_i$ with a bounded gain error. In the nominal proof this relation is exact; under modeling uncertainty it is exact up to a bounded disturbance $d_i(t)$ with $|d_i(t)|\le \bar d$.
\end{assumption}

\section{Convergence Under DoS and Detected FDI}

The convergence analysis is now a switching-graph problem. DoS removes unavailable links through $\gamma_{ij}=0$, and detected FDI removes corrupted links through $\sigma_{ij}=0$. Hence, the only graph that enters the controller is $\mathcal{G}_r(t)$.

\begin{assumption}[Trusted connectivity after isolation]
There exists a constant $\underline{\lambda}>0$ such that, during trusted connected intervals,
\begin{equation}
    \lambda_2(L_r(t))\ge \underline{\lambda}.
    \label{eq:lambda_lower}
\end{equation}
When $\mathcal{G}_r(t)$ is disconnected, $\lambda_2(L_r(t))$ is set to zero in the convergence bound.
\end{assumption}

\begin{assumption}[Nonexpansive fallback]
When the trusted graph is disconnected because of DoS or FDI isolation, the cooperative term is either computed on the remaining trusted connected components or set to zero on unsafe links. This fallback does not increase the impact-time disagreement energy.
\end{assumption}

Define the projection matrix
\begin{equation}
    M=I-\frac{1}{N}\mathbf{1}\mathbf{1}^{\top}
\end{equation}
and the disagreement vector
\begin{equation}
    \tilde T=MT.
\end{equation}
The Lyapunov function is
\begin{equation}
    V(t)=\frac{1}{2}\tilde T^{\top}(t)\tilde T(t).
    \label{eq:lyapunov}
\end{equation}

\begin{theorem}[Exponential convergence under trusted connectivity]
Consider the trusted-graph control law \eqref{eq:linear_sync}. Suppose that detected FDI links and DoS-blocked links are excluded according to \eqref{eq:trusted_adjacency}. Then the disagreement energy satisfies
\begin{equation}
    V(t)
    \le
    V(0)
    \exp
    \left[
    -2k
    \int_0^t
    \lambda_2(L_r(s))\,ds
    \right].
    \label{eq:exp_bound}
\end{equation}
Consequently, if
\begin{equation}
    \int_0^\infty \lambda_2(L_r(s))\,ds=\infty,
    \label{eq:cumulative_connectivity}
\end{equation}
then $T_i(t)-T_j(t)\to0$ for all normal vehicles. For a prescribed terminal time $t_f$, the sufficient condition
\begin{equation}
    \int_0^{t_f}
    \lambda_2(L_r(s))\,ds
    \ge
    \frac{1}{2k}\ln\frac{V(0)}{\varepsilon}
    \label{eq:finite_error_condition}
\end{equation}
guarantees $V(t_f)\le\varepsilon$.
\end{theorem}

\begin{proof}
Because $L_r(t)\mathbf{1}=0$, one has $ML_r(t)=L_r(t)M=L_r(t)$ for an undirected trusted graph. During trusted intervals governed by \eqref{eq:linear_sync},
\begin{equation}
    \dot{\tilde T}
    =
    M\dot T
    =
    -kML_rT
    =
    -kL_r\tilde T .
\end{equation}
Therefore,
\begin{equation}
    \dot V
    =
    \tilde T^\top\dot{\tilde T}
    =
    -k\tilde T^\top L_r\tilde T .
\end{equation}
For a connected trusted graph,
\begin{equation}
    \tilde T^\top L_r\tilde T
    \ge
    \lambda_2(L_r)\|\tilde T\|^2
    =
    2\lambda_2(L_r)V.
\end{equation}
Hence,
\begin{equation}
    \dot V
    \le
    -2k\lambda_2(L_r)V.
\end{equation}
During disconnected or unsafe intervals, the nonexpansive fallback gives $\dot V\le0$, which is the same inequality with $\lambda_2(L_r)=0$. Thus the inequality holds for all time. Applying the comparison lemma gives \eqref{eq:exp_bound}. Conditions \eqref{eq:cumulative_connectivity} and \eqref{eq:finite_error_condition} follow directly from \eqref{eq:exp_bound}.
\end{proof}

\begin{corollary}[Fixed-time convergence with accumulated trusted time]
Under \eqref{eq:fixed_time_sync}, suppose that the trusted connected graph satisfies \eqref{eq:lambda_lower} during connected intervals and that the fallback is nonexpansive otherwise. If there exist constants $c_1,c_2>0$ such that
\begin{equation}
    \dot V
    \le
    -\delta_r(t)
    \left[
    c_1 V^{\frac{1+\alpha}{2}}
    +
    c_2 V^{\frac{1+\beta}{2}}
    \right],
    \label{eq:fixed_vdot}
\end{equation}
where $\delta_r(t)=1$ on trusted connected intervals and $\delta_r(t)=0$ otherwise, then $V$ reaches zero once
\begin{equation}
    \int_0^t \delta_r(s)\,ds
    \ge
    \frac{2}{c_1(1-\alpha)}
    +
    \frac{2}{c_2(\beta-1)}.
    \label{eq:ft_condition}
\end{equation}
\end{corollary}

\begin{proof}
For $V>0$, set $z=\sqrt{V}$. From \eqref{eq:fixed_vdot},
\begin{equation}
    \dot z
    \le
    -\frac{\delta_r(t)}{2}
    \left(c_1 z^\alpha+c_2 z^\beta\right).
\end{equation}
Using the accumulated trusted time $\tau_r(t)=\int_0^t\delta_r(s)ds$ as the time variable gives
\begin{equation}
    \frac{dz}{d\tau_r}
    \le
    -\frac{1}{2}
    \left(c_1 z^\alpha+c_2 z^\beta\right).
\end{equation}
The standard fixed-time bound yields \eqref{eq:ft_condition}.
\end{proof}

\section{Connection With Probabilistic Safe Communication Time}

If the DoS process is random, the safe communication duration can be described probabilistically. For example,
\begin{equation}
    T_s
    =
    T\sum_{k=0}^{\mathcal{E}}
    F(k)(1-\rho_c)^k\rho_c^{\mathcal{E}-k},
    \label{eq:prob_safe_time}
\end{equation}
where $\mathcal{E}$ is the number of communication edges, $F(k)$ denotes the number of connected subgraphs obtained when exactly $k$ edges are preserved, and $\rho_c$ is the edge failure probability. The notation $\rho_c$ is used here to avoid conflict with the finite-time exponent $p$.

Equation \eqref{eq:prob_safe_time} should be interpreted carefully. If $T_s$ is an expected value, it cannot by itself prove deterministic finite-time convergence. A deterministic theorem requires a lower bound on the accumulated trusted connectivity in \eqref{eq:finite_error_condition}. In contrast, a probabilistic theorem can be stated in terms of
\begin{equation}
    \mathbb{P}\left\{
    \int_0^{t_f}\lambda_2(L_r(s))ds
    \ge
    \frac{1}{2k}\ln\frac{V(0)}{\varepsilon}
    \right\}.
\end{equation}
This probability quantifies the likelihood that the vehicles complete time-to-go synchronization before interception under random link failures.

\section{Simulation Plan}

The following cases can be used to verify the proposed framework.

\subsection{No-Attack Baseline}
The first case verifies that the proposed guidance law reduces to the nominal cooperative guidance law when $\gamma_{ij}=1$ and $f_{ij}=0$ for all links.

\subsection{DoS-Only Case}
Several communication links are blocked over prescribed time intervals. The zero-bias strategy, the holding-type virtual leader, and the target-oriented virtual leader should be compared.

\subsection{FDI-Only Case}
Bias, sinusoidal, state-dependent, and slow-drift FDI signals are injected into selected links. The physical trust $\rho_{ij}^{\mathrm{phy}}(t)$, the group-consistency or GMM trust $\rho_{ij}^{\mathrm{gmm}}(t)$, the distribution trust $\rho_{ij}^{\mathrm{kl}}(t)$, and the final binary isolation decision $\sigma_{ij}(t)$ should be plotted to show when corrupted links are removed from the trusted graph. This case should also compare the proposed multi-evidence isolation rule with a single residual detector.

\subsection{Hybrid DoS and FDI Case}
Some links are blocked by DoS, while other available links are corrupted by FDI. This case is the main scenario for validating the trusted graph construction in \eqref{eq:trusted_adjacency}, where DoS-blocked and FDI-detected links are both excluded before the cooperative guidance command is computed.

\subsection{Boundary Test on Effective Communication Time}
The DoS duty cycle and FDI intensity are varied to test whether the convergence behavior changes consistently with the cumulative trusted-connectivity conditions \eqref{eq:finite_error_condition} and \eqref{eq:ft_condition}.

\subsection{Ablation Study}
The ablation study should remove one module at a time: physical feasibility, group-consistency/GMM trust, windowed residual statistics, link isolation, node isolation, and zero-bias fallback. The expected metrics include miss distance, impact-time disagreement, $V(t)$, $\int_0^t\lambda_2(L_r(s))ds$, trust-weight evolution, false alarm rate, missed detection rate, isolated-link count, and command magnitude.

\section{Possible Contributions}

The method can be written as the following contributions:
\begin{enumerate}
    \item A hybrid DoS-FDI attack model is established for cooperative guidance, simultaneously describing missing neighbor information and corrupted neighbor information.
    \item A multi-evidence FDI trust evaluation mechanism is proposed by combining physical feasibility, group-consistency clustering, and windowed distribution divergence, reducing the dependence on a single prediction residual.
    \item A trusted-graph isolation mechanism is proposed: DoS-blocked links and FDI-detected links are removed from the cooperative graph before they can affect the guidance command.
    \item Exponential and fixed-time convergence conditions are derived in terms of accumulated trusted connectivity, clarifying when synchronization before interception can still be guaranteed under hybrid cyber attacks.
\end{enumerate}

\section{Technical Boundaries}

Several limitations should be stated explicitly in the final manuscript. First, the physical feasibility interval in \eqref{eq:physical_interval} must be constructed from valid bounds on acceleration, target maneuver, and field-of-view constraints; otherwise the physical trust score may become overly conservative. Second, GMM-based or median-based trust requires enough neighbor redundancy to separate normal and suspicious links. If too many vehicles are attacked simultaneously, the isolation result may remove too much of the communication graph. Third, windowed residual statistics depend on the quality of the nominal residual model and the window length. A short window reacts quickly but may increase false alarms, whereas a long window is smoother but slower. Fourth, link isolation protects the controller from detected corrupted data, but convergence still requires sufficient trusted connectivity after isolation. Finally, if field-of-view or nonsingularity auxiliary functions drive the effective impact-time control gain to zero, fixed-time convergence cannot be strictly guaranteed. In that case, the result should be weakened to asymptotic convergence, convergence to a small neighborhood, or finite-time convergence under an additional gain lower-bound condition.

\section{Conclusion}

This draft provides a complete framework for handling DoS and FDI attacks in cooperative guidance. The key is to avoid allowing unavailable or corrupted neighbor data to enter the cooperative guidance law. DoS is handled as link unavailability, whereas detected FDI is handled by isolating the corrupted link or, in conservative cases, the compromised node. The resulting trusted graph is used to construct the impact-time synchronization error and the cooperative guidance command. Under sufficient accumulated trusted connectivity after isolation, the predicted impact times converge before interception or reach a prescribed disagreement bound at the terminal time.

\balance
\end{document}
